\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[full]{textcomp}
\usepackage{CJKutf8}
\usepackage[lf]{ebgaramond}
% \usepackage[scaled,swashQ]{garamondx}
\usepackage[T1]{fontenc}

\usepackage{enumitem}
\usepackage[a4paper,left=.9in, right=.9in, top=1.5in, bottom=1.5in]{geometry}
\usepackage{url}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}

% package settings
\usepackage[
    hidelinks,
    pdfnewwindow=true,
    pdfauthor={Nived},
    pdftitle={Curriculum Vitae of Xovee Xu},
]{hyperref}

\pagestyle{headings}
\markright{\textbf{Xovee Xu}}

\setlength\parindent{2em}

\thispagestyle{empty}

% define cv section
\newcommand{\cvsection}[1]{\section*{\rmfamily#1}}
\newcommand{\cvsubsection}[1]{\subsection*{\rmfamily\hspace{1.6em}#1}}

% begin
\begin{document}

% name
\begin{center}
    \Huge{
    \rmfamily
    \textbf{Sai Nived Chandanam}}
\end{center}
\vspace{20pt}


\setlength{\parskip}{1pt}
\renewcommand{\arraystretch}{1.25}

% Contact Information

\noindent School of Computer Science and Engineering \hfill (+86) 123-456-789

\noindent University of Electronic Science and Technology of China (UESTC)\hfill \href{mailto:xovee@std.uestc.edu.cn}{\texttt{xovee@std.uestc.edu.cn}}

\noindent Chengdu, Sichuan 610054, China\hfill \url{https://xovee.cn}


\setlength{\parskip}{3pt}



% Education
\cvsection{Education}
\indent

\textbf{THE UNIVERSITY OF TEXAS AT DALLS}, Richardson, Texas \hfill Expected Dec 2024

Master of Science in Computer Enginnering

\indent

\textbf{SRM UNIVERSITY}, AP, India \hfill April 2022

Bachelor of Technology in Electronics and Computer Enginnering\hfill\textbf{GPA 8.6/10}

%Computer Skills
\cvsection{COMPUTER SKILLS}
\indent

Languages :  Python, C, HTML, CSS, VHDL, Latex

Operating Systems : Windows, Linux

Tools : Xilinx, EDA, Cadence Virtuoso, Blender, Premiere Pro



% academic Projects
\cvsection{Academic Projects}

\cvsubsection{Image Enhancement Using VHDL}
%\indent

The project basically deals with image enhancement techniques. The enhancement operations are done using VHDL. The main theme is to enhance image using Threshold Operation, Invert Operation, Brightness Operation.


\cvsubsection{Design and Implementation of SPI Protocol:}
\indent

O Design and development of SPI by using the verilog code and creating the Master and Slave. The Finite StateMachines (FSM) and the state diagrams of both Master and Slave are used for verification purposes. From the RTL synthesis the schematic diagram and the synthesis results are covered.


\cvsubsection{HDR Image Processing:}
\indent

The project involves alignment and merging of 30 burst RAW images into a single HDR image. Later various post-processing are applied to the image which includes tone mapping, lens shading correction, white balancing etc. Better noise reduction and high dynamic range is observed.

\cvsubsection{True Random Number Generator: }
\indent

TRNG’s are used in cryptography and simulations for conditions in background noise that impact the system. For a PUF it's very unlikely to make another device alike due to various intrinsic properties during the manufacturing process. PUF’s have various applications which include low-cost authentication, secure key generation.




% publication
\section*{Publication}

\cvsubsection{Refereed Journal Articles}

\begin{enumerate}[resume]
    \item Fan Zhou, Xovee Xu*, Goce Trajcevski, Kunpeng Zhang. 2021. A survey of information cascade analysis: Models, predictions, and recent advances. \textit{ACM Computing Surveys (CSUR)}, vol. 54, no. 2, article 27, 36 pages, Mar 2021, doi:\href{https://xovee.cn/html/paper-redirects/csur2021.html}{10.1145/3433000}, \href{https://arxiv.org/abs/2005.11041}{arXiv:2005.11041}
\end{enumerate}

\cvsubsection{Refereed Conference Articles}

\begin{enumerate}[resume]
    \item Fan Zhou, Xovee Xu, Kunpeng Zhang, Goce Trajcevski, and Ting Zhong*. 2020. Variational information diffusion for probabilistic cascade prediction. IEEE International Conference on Computer Communications (INFOCOM), Virtual Conference, Jul 6-9, 2020, pp. 1618-1627, doi:\href{https://doi.org/10.1109/INFOCOM41043.2020.9155349}{10.1109/INFOCOM41043.2020.9155349}
    \newline \textbf{\color{red}INFOCOM 2020 Student Conference Award}
\end{enumerate}




% talks
\cvsection{Invited Talk}
\indent 

University of CV, Dept. of Linguistics, 2077 



% teaching experience 
\cvsection{Teaching Experience}
\indent

\textbf{C Programming Language}\hfill Spring 2020

\hspace{2em}Teaching Assistant, with Prof. Ting Zhong, at UESTC

\textbf{Software Project Management}\hfill Summer 2019

\hspace{2em}Teaching Assistant, with Prof. Gianmario Motta (University of Pavia), at UESTC




% industrial experience
% \section*{Industrial Experience}
% \indent

% \textbf{Strawberry Inc.}, Beijing, China

% \hspace{2em}Co-funder, 2077 - 

% \textbf{Delicious Mango Holdings Ltd.}, London, UK

% \hspace{2em}\LaTeX~Engineer Intern, 2076 - 2077

% \textbf{CV Agency Co. Ltd.}, Hawaii, USA

% \hspace{2em}CV Broker, 2075 - 2076
% \begin{itemize}[leftmargin=5em, topsep=0pt, itemsep=0pt]
%     \item Helped a three-year old child create her first CV
%     \item Hilight 2 ...
%     \item Hilight 3 ...
% \end{itemize}




% language
\cvsection{Language}
\indent

Native Chinese (Mandarin \& Northern Shaanxi Dialect)

Fluent English




% reference 
\cvsection{Reference}
\indent

\textbf{Dr. John Smith}, Professor and Chair, Dept. of Curriculum Vitae, University of Standard

\hspace{2em}(+86) 181-xxxx-xxxx \hspace{2em} \url{xovee@ieee.org}


% other things
\cvsection{Any Other Sections}
\indent 

Wow! A lengthy CV!


\vfill

\section*{\hfill\color{OliveGreen}\today}

\end{document}